Stage-Splitting a Modal Language

### 2014-10-13 paper/splitting.tex
quick incremental improvement to splitting rules descriptions

\ur{Explain the rules.  This is the most important part of the
  paper. Work needed here.}
Every $\splittwosym$ rule works by bundling the precomputations of the constituent parts, and
then unbundling them with a pattern.
The rules for splitting $\next$, $\prev$, and $\pause$ are given in \ref{fig:termSplitOne}.
The rule for $\next$ simply tuples up the precomputation of its subexpression with a trivial immediate result,
while the rule for $\prev$ projects the combined result of its subexpression to just the precomputation.
The $\pause$ rule treats the entire combined result of its subexpression as a precomputation, 
and projects out the integer result in the residual.%
\footnote{The residual of an integer expression is usually trivial, 
but we have to include it here for termination purposes.}

>>>>

The $\splittwosym$ rules are conceptually simple and almost all very similar.  
As mentioned before, the only responsibility of $\splittwosym$ is to lift out the precomputation
from contained stage \bbone\ code into a single expression $p$, 
leaving a residual $l.r$ to interpret the results of that precomputation.
Since base types and variables have no stage \bbone\ content, their precomputation is trivial;
that is, $p$ is a unit value and $l$ is never used in $r$.
At every other expression except $\prev$, the $\splittwosym$ rule works by bundling 
the precomputations of the constituent parts, and then unbundling them with a pattern,
with the residual precisely resembling the original expression.

The rule for $\next$ simply tuples up the precomputation of its subexpression with a trivial immediate result,
while the rule for $\prev$ projects the combined result of its subexpression to isolate the precomputation.
It may seem like this $\prev$ rule is throwing information away, but we well show later that the first component 
of the evaluated form of $c$ in the $\prev$ rule must always be unit.
The $\pause$ rule treats the entire combined result of its subexpression as a precomputation, 
and projects out the integer result in the residual.%
\footnote{The residual of an integer expression is usually trivial, 
but we have to include it here for termination purposes.}
